---
output: 
  pdf_document:
    keep_tex: yes
    fig_caption: yes
    number_sections: yes
geometry: margin=2.54cm
title: "Insert title of project here"
subtitle: "Web address for GitHub repository"
author: "Name"
fontsize: 12pt
mainfont: Times New Roman

---

\newpage
\tableofcontents 
\newpage
\listoftables 
\newpage
\listoffigures 
\newpage

```{r setup, include=FALSE}
# Set your working directory
getwd()
setwd('c:/Users/Jiawei Liang/Documents/EDA-Fall2022/Project/RawData/')
# Load your packages
library(tidyverse)
library(lubridate)
library(dplyr)
library(cowplot)
library(ggplot2)
library(reshape2)
# Set your ggplot theme
theme_default <- theme_set(theme_bw())
theme_set(theme_default)
# Load your datasets
major_source <- read.csv('consumption-major-source.csv', stringsAsFactors = TRUE)
natural_gas_production <- read.csv('natural_gas_productionus.csv', stringsAsFactors = TRUE)
US_Carbon_emission <- read.csv('united-states-carbon-co2-emissions.csv', stringsAsFactors = TRUE)
Energy_consumption_sector<- read.csv('primary-energy-consumption.csv', stringsAsFactors = TRUE)
Electricpowercarbonemissions<- read.csv('emissionfueltype.csv', stringsAsFactors = TRUE)
Newdata <- read.csv("Newdata.csv")
electricitygeneration<- read.csv('electricity-generation.csv', stringsAsFactors = FALSE)
electricitygeneration$Year <-as.numeric(as.character(electricitygeneration$Year)) 
```


# Rationale and Research Questions



\newpage

# Dataset Information



\newpage

# Exploratory Analysis 

Q1: The change of the emissions in US. 
```{r}
ggplot() +
  theme_bw() +
  geom_segment(data = US_Carbon_emission, 
               aes(x =  Date, 
                   y = Total, 
                   xend = Date, 
                   yend = -30), 
               size = 4, 
               colour =  " orange")+
      scale_y_continuous(breaks=c(1e+06,2e+06,3e+06,4e+06,5e+06,6e+06))+
  scale_x_continuous(breaks=seq(1991,2020,2) )+
  labs(title = "Total Greenhouse Gas Emissions in U.S")+
       xlab("Year")+
       ylab("Total Carbon Emissions(Metric Tons)")
       
```
per
```{r}
carbon_emissions_per_capita <- ggplot(US_Carbon_emission) +
  geom_line(aes(x = Date, y = Per.Capita),colour="blue")+
  scale_x_continuous(breaks=seq(1990,2021,2) )+
   xlab("Year")+
       ylab("Emission in Ton")+
  labs(title = "Carbon emissions per capita in U.S")
print(carbon_emissions_per_capita)
```



Energy structure:
```{r}
Energy_Structure <- ggplot( major_source, aes(x=Year,y=Consumption, fill = Source ))+
  scale_x_continuous(breaks=seq(1990,2021,2) )+
  labs(title = "Major Source Consumption in U.S")+
  xlab("Year")+
       ylab("Consumption in quadrillion Btu")+
  geom_area()
  
print(Energy_Structure)
```
gas production:
```{r}
Gas_production <- ggplot(natural_gas_production) +
  geom_line(aes(x = Year, y = Production))+
  scale_x_continuous(breaks=seq(1998,2021,2) )+
   xlab("Year")+
       ylab("Consumption in tens of billions cubic")+
  labs(title = "Consumption of natural gas in the United States")
print(Gas_production)
 
```
which sector use more energy
```{r}
Energy_Structure <- ggplot( Energy_consumption_sector, aes(x=Year,y=Consumption, fill = Sector ))+
  scale_x_continuous(breaks=seq(1990,2020,5) )+
  labs(title = "Primary energy consumption in the United States")+
       xlab("Year")+
       ylab("Consumption in quadrillion Btu")+
  geom_area()
print(Energy_Structure)
```
Electric power emissions
```{r}
  
ggplot(electricitygeneration,aes(x=Year, y=Generation,fill=Type))+
 geom_area(stat="identity",position = 'stack')



```

```{r}
ggplot(electricitygeneration,aes(x=Year, y=Generation,fill=Type))+
 geom_bar(stat="identity",position = 'stack')

```


\newpage

# Analysis



## Question 1: <insert specific question here and add additional subsections for additional questions below, if needed>

## Question 2: 




\newpage

# Summary and Conclusions


\newpage

# References
<add references here if relevant, otherwise delete this section> 
